\textbf{universal corpus}

### 2014-04-27 docs/computEL-final/concl.tex
edited final paragraph in conclusion as commented.

SeedLing will be made available initially through the websites of the authors, as we have yet to properly address the question of long-term access; we welcome ideas or collaborations along these lines. In addition, we are releasing a Python API which allows programmatic access to the data and is easily compatible with the analysis tools available from the Natural Language ToolKit \cite{BirdKleinLoper09} \footnote{\url{https://github.com/alvations/SeedLing}}. The API also facilitates access to information from both Ethnologue and WALS: a user can extract information about languages, language classification, endangerment status, typological features, and so on. Finally, we will make our clustering scripts freely available.

% The API also includes a feature to access information on a language from Ethnologue and/or WALS. This feature queries the Ethnologue and/or WALS site both in real-time when internet connection is available and from a local copy of the information offline.

>>>>

SeedLing (and the API) is currently available via a GitHub repository.\footnote{https://github.com/alvations/SeedLing} We have yet to fully address questions of long-term access, and we welcome ideas or collaborations along these lines.
